Network Configuration Synthesis with Abstract Topologies \vspace{1cm}

### 2017-03-15 paper/abstraction/appendix.tex
more edits

\begin{defn}
Given a regular expression $r$ over abstract locations, homomorphism $f$, a nonempty set of locations $L$, and a finite state machine $M^A = (\Sigma,Q,q_0,\sigma^A,F^A)$, we construct a concrete state machine $M = (\Sigma, Q, q_0, \sigma, F)$ for the concretized policy $con(r,\Gamma, f) \cap \EndR(L)$ in the following way:

@@

\begin{lem}
  The homomorphism $f$ is lifted to a new homomorphism $f_{pg}$ over the product graphs in the following way:
  \[ \begin{array}{rcl}
    f_{pg}( start ) & = & start^A  \\
    f_{pg}( (l,q_1,\ldots,q_n) ) & = & (f(l),q_1,\ldots,q_n) \\
  \end{array} \]

  Now we prove that $f_{pg}: G' \rightarrow G'^A$ is a valid homomorphism
  \begin{proof}
    From Lemma 4, $(f(l),q_1,\ldots,q_n)$ is a valid node in $PG^A$ since both automata share the same states. 
    %
    Assume there is an edge in $PG$ from $x=(l,q_1,\ldots,q_n)$
    to $y=(l',q_1',\ldots,q_n')$. We know that $f(x) = (f(l),q_1,\ldots,q_n)$ and $f(y) = (f(l'),q_1',\ldots,q_n')$.
    %
    From the construction of PG, we know that $\sigma_i(q_k, l) = q_k'$. 
    Also from the construction of the abstract automata, we also know that $\sigma_i(q_k, l) = q_k' \iff \sigma^A_i(q_k, f(l)) = q_k'$. Therefore, we can conclude that $\sigma^A_i(q_k, f(l)) = q_k'$. However, from the definition of $PG^A$, this means that there must be an edge in $PG^A$ for ($f(x),f(y)$).
  \end{proof}
\end{lem}

@@

  \begin{proof}
    Assume $n = (l,q_1,\dots,q_k)$. We know that $f_{pg}(n) = (f(l),q_1,\dots,q_k)$. 
    We also know that $q_i \in F \iff q_i \in F^A$. 
    By the definition of the ranking function $\Rank$, then 
    $\Rank(n) = \{ i ~\vert~ q_i \in F \} = \{ i ~\vert~ q_i \in F^A \} = \Rank^A(N)$.
  \end{proof}

@@

    \noindent
    From Lemma 6, and $m' \geq_{rank} m$ we know that $f_{pg}(m') \geq_{rank} f_{pg}(m)$. 
    From Lemma 8, there is a transition $\trans{f(n)}{f(n')}{f(l)}$.

@@

    \noindent
    Thus if there is transition $\trans{m'}{n'}{b}$, then there is also a transition $\trans{m}{n}{b}$. 
    Lemma 6 together with the assumption $N' \geq_{rank} N$ and the fact that $\Rank(n) = \Rank(N)$ lets us conclude that $n' \geq_{rank} n$.

@@

\vspace{1em}
Lemma 9 tells us that the total ordering between node preferences is preserved under the lifted graph homomorphism $f_{pg}$. 
We use this fact to define the local preference function ($\Pref : V \rightarrow \mathbb{N}$) that maps product graph nodes to numbers reflecting the total ordering such that $\Pref(m) = \Pref(f(m))$ for all product graph nodes $m$.

\vspace{1em}
\begin{defn}
  Assign $\Pref(m) = \Pref^A(f_{pg}(m))$ as increasing integers starting from 0 according to the total ordering for $\leq$.
  From Lemma 9, we know that $\Pref$ and $\Pref^A$ preserve the total ordering since: $\Pref(m) \leq \Pref(m') \iff m \leq m'$ and $\Pref(f_{pg}(m)) \leq \Pref(f_{pg}(m')) \iff f_{pg}(m) \leq f_{pg}(m')$.
\end{defn}

>>>>

\begin{defn}
Given a regular expression $r$ over abstract locations, homomorphism $f$, a nonempty set of locations $L$, and a finite state machine $M^A = (\Sigma,Q^A,q_0,\sigma^A,F^A)$, we construct a concrete state machine $M = (\Sigma, Q, q_0, \sigma, F)$ for the concretized policy $con(r,\Gamma, f) \cap \EndR(L)$ in the following way:

@@

\begin{lem}
  For any node $n = (l,q_1,\ldots,q_k)$ in $PG$ there exists a node $f(n) = (f(l),q_1,\ldots,q_k)$ in $PG^A$.
  \begin{proof}
    Consider a path of length k in $PG$ to node $n$. The proof proceeds by induction on the path length $k$, if $n$ is connected to $start$, then $q_i = q_{0_i}$. Since there are no transitions back to the initial state, there must be a node $f(n) = (f(l), q_{0_1}, \ldots, q_{0_1})$ or else there is a contradiction for Lemma 1. For the inductive case, if $n$ is the kth hop along the path, then it has an inbound edge from neighbor $k-1$. Call this neighbor $m$. Then $(m,n)$ is an edge in $PG$, there is a node $f(m)$ with the same states. From the graph homomorphism, we know that $(f(m),f(n))$ must be an edge in $PG^A$ and since $f(m)$ has the same states as $m$, by the construction of the automata, $f(n)$ will have the same states as $n$.
  \end{proof}
\end{lem}

\begin{lem}
  The homomorphism $f$ can be lifted to a new homomorphism $f_{pg}$ over the product graphs in the following way:
  \[ \begin{array}{rcl}
    f_{pg}( start ) & = & start^A  \\
    f_{pg}( (l,q_1,\ldots,q_n) ) & = & (f(l),q_1,\ldots,q_n) \\
  \end{array} \]

  Now we prove that $f_{pg}: G' \rightarrow G'^A$ is a valid homomorphism
  \begin{proof}
    From Lemma 5, $(f(l),q_1,\ldots,q_n)$ is a valid node in $PG^A$. 
    %
    Assume there is an edge in $PG$ from $x=(l,q_1,\ldots,q_n)$
    to $y=(l',q_1',\ldots,q_n')$. We know that $f(x) = (f(l),q_1,\ldots,q_n)$ and $f(y) = (f(l'),q_1',\ldots,q_n')$.
    %
    From the construction of PG, we know that $\sigma_i(q_k, l) = q_k'$. 
    Also from the construction of the abstract automata, we also know that $\sigma_i(q_k, l) = q_k' \iff \sigma^A_i(q_k, f(l)) = q_k'$. Therefore, we can conclude that $\sigma^A_i(q_k, f(l)) = q_k'$. However, from the definition of $PG^A$, this means that there must be an edge in $PG^A$ for ($f(x),f(y)$).
  \end{proof}
\end{lem}

@@

  \begin{proof}
    Assume $n = (l,q_1,\dots,q_k)$. From Lemma 6, we know $f_{pg}(n) = (f(l),q_1,\dots,q_k)$. 
    We also know that $q_i \in F \iff q_i \in F^A$. 
    By the definition of the ranking function $\Rank$, then 
    $\Rank(n) = \{ i ~\vert~ q_i \in F \} = \{ i ~\vert~ q_i \in F^A \} = \Rank^A(N)$.
  \end{proof}

@@

    \noindent
    From Lemma 7, and $m' \geq_{rank} m$ we know that $f_{pg}(m') \geq_{rank} f_{pg}(m)$. 
    From Lemma 9, there is a transition $\trans{f(n)}{f(n')}{f(l)}$.

@@

    \noindent
    Thus if there is transition $\trans{m'}{n'}{b}$, then there is also a transition $\trans{m}{n}{b}$. 
    Lemma 7 together with the assumption $N' \geq_{rank} N$ and the fact that $\Rank(n) = \Rank(N)$ lets us conclude that $n' \geq_{rank} n$.

@@

\vspace{1em}
Lemma 10 tells us that the total ordering between node preferences is preserved under the lifted graph homomorphism $f_{pg}$. 
We use this fact to define the local preference function ($\Pref : V \rightarrow \mathbb{N}$) that maps product graph nodes to numbers reflecting the total ordering such that $\Pref(m) = \Pref(f(m))$ for all product graph nodes $m$.

\vspace{1em}
\begin{defn}
  Assign $\Pref(m) = \Pref^A(f_{pg}(m))$ as increasing integers starting from 0 according to the total ordering for $\leq$.
  From Lemma 10, we know that $\Pref$ and $\Pref^A$ preserve the total ordering since: $\Pref(m) \leq \Pref(m') \iff m \leq m'$ and $\Pref(f_{pg}(m)) \leq \Pref(f_{pg}(m')) \iff f_{pg}(m) \leq f_{pg}(m')$.
\end{defn}
